Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-29 writing/CONUS_AOD.qmd
Moved the IVs table to the paper supplement.
Added some inline code to replace deleted table columns.

@tbl-cv-overall includes the performance metrics for the full cross-validated training data set. Here **raw** is Collection 6.1 MAIAC AOD 470nm; **ground** is AERONET AOD interpolated to 470nm; and **corrected** is MAIAC after applying an XGBoost-modeled correction term.

>>>>

@tbl-cv-overall includes the performance metrics for the full cross-validated training data set. `r sdn = \(x) sqrt(mean((x - mean(x))^2)); f = \(x) sprintf("(SD %.03f)", sdn(dt[[x]])); "";` Here **raw** is Collection 6.1 MAIAC AOD 470nm `r f("y.sat")`; **ground** is AERONET AOD interpolated to 470nm `r f("y.ground")`; and **corrected** is MAIAC after applying an XGBoost-modeled correction term `r f("y.ground.pred")`. The ground values are correlated `r dt[, sprintf("%+.03f", cor(y.ground, y.sat))]` with the raw values and `r dt[, sprintf("%+.03f", cor(y.ground, y.ground.pred))]` with the corrected values.
